Quantum Computing and its Implications on Digital Security

### 2021-12-12 paper.tex
feat: Improve Josephson junctions

\begin{subsection}{Josephson Junctions}
A Josepson junction quantum computer is a Cooper pair box,
which is a small superconducting island electrode weakly coupled to a bulk superconductor. 
In literature, the Josephson junctions are also refered to as superconducting quantum computers.
Weak coupling between the superconductors create a Josephson junction between them which behaves as a capactor. 
If the Cooper box is as small as a quantum dot, 
the charging current breaks into discrete transfer of individual Cooper pairs. 
Ultimately, it is possible to just transfer a single Cooper pair across a junction. 
Qubits in Josephson junction quantum computers are controlled electrically which results in them being interesting for future developments.

In Physics, the Josephson effect is a phenomenon that occurs when two superconductors are placed in proximity, 
with some barrier or restriction between them. 
The Josephon effect produces a current, known as supercurrent, that flows continuosly without any voltage applied. 
This current thorught the junction occurs by quantum tunneling. 
This is used to create a non-linear inductance which is essential for qubit design, 
as it allows a design of anharmonic oscialltors. 
A quantum harmonic oscillator cannot be used as a qubit, 
as there is no way to address only two of its states. 
\end{subsection}

>>>>

\begin{subsection}{Josephson Junction}
As Martinis and Osborne explain in their paper, 
the Josephson effect is a phenomenon that occurs when two superconductors are seperated 
by some barrier or restriction between them, which is thin enough that electrons can tunnel through the barrier using quantum-mechanics. 
This tunneling produces a current, known as supercurrent, that flows continuosly without any voltage applied. 
This is used to create a non-linear inductance and design the qubits. 
Wendin and Shumeiko mention \cite{shumeiko} many ways to realize qubits in Josephson junction based quantum computers. 
The simplest of which is to realize qubits in Josepshon junctions by comparing energy levels of josepshon energy to the normal charging energy. 
The josephson energy comes from kinetic energy of the tunneling electrons.

Martinis and Osborne state that Josephson junction quantum computers are especially interesing because superconductor could provide long coherence times and because increasing the number of qubits should be straightforward.

Qubits in Josephson junction quantum computers are controlled electrically which results in them being interesting for future developments.
\end{subsection}
